%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}Sherkeem Duprey

347-423-3123 | sherkeemduprey@gmail.com | linkedin.com/in/sherkeem-duprey/ | github.com/Sduprey18

EDUCATION
University of Rochester Rochester, NY
Bachelor of Arts in Computer Science Aug. 2022 - May 2026

Relevant Coursework:
Data Structures & Algorithms, Web Programming, Computation Formal Systems, Artificial Intelligence,
Mobile App Development

EXPERIENCE
Fullstack Software Engineering Intern May 2025
Intuit Mountain View , CA
¢ Incoming summer 2025
HVAC Automation Intern June 2024 — August 2024
Merck Rahway, NJ

¢ Facilitated data analysis and automated processes through the implementation of Pi Displays for 10 buildings,
resulting in 30% increase in HVAC cooling efficiency and real-time monitoring of key metrics.

« Developed a PowerApp to simplify disabled point reporting and viewing for 900+ points per month incorporating,
PowerBI integration, and PI WebAPI for accurate tag location and validation.

¢ Identified and addressed over 300 undocumented points in the PI system, ensuring accurate and comprehensive
documentation for all data points.

XR Applications Developer Sep. 2023 — Present
Studio X Rochester, NY
¢ Spearheaded the advancement of the coding team in Aurum, the in-house alchemy VR game, creating C# scripts
to create game functionality, exhibited to over 500 patrons at exclusive events.
¢ Teaching and providing support for over 60 workshops, attended by over 1,700 participants, through the academic
year, on topics such as Unity, Blender and XR development.

¢ Provided technical consultations in-person and on Discord for XR development.

PROJECTS

Java Street Mapping | Java Github link
« Developed a Java program for map processing, to determine the fastest/shortest destination route.
¢ Utilized my own custom built HashMap, and LinkedLists for graph representation.
¢ Enacted Dijkstra’s algorithm for finding the shortest path.
¢ Implemented Kruskal’s algorithm for finding the minimum weight spanning tree.

Finite Automata String Validator | C Github link

¢ Developed a C-based application to simulate Deterministic Finite Automata (DFA) and Nondeterministic Finite
Automata (NFA) for string validation tasks.

¢ Built interactive REPL functions for both DFA and NFA simulations, allowing dynamic user input to test string
acceptance.

¢ Utilized custom C structures and functions to manage states, transitions, and string evaluation for both automata
types.

¢ Utilized custom C structures and functions, improving automata processing efficiency by 20% through optimized
state transitions and reduced computational overhead.

TECHNICAL SKILLS & ORGANIZATIONS

Languages: Swift, Java, Python, C/C#, JavaScript, HTML/CSS

Frameworks: React, Node.js, Flask, SwiftUI

Developer Tools: Git, Docker, Aveva PI System, VS Code, Visual Studio, Xcode, PlasticSCM, Unity
Organizations: ColorStack, National Society of Black Engineers, Participant of Amazon’s Campus Summer Series,
Google Software Engineering Program (G-SWEP)
